Mortality Trend Among Shelter Residents: 

### 2024-09-27 paper/paper.qmd
made change to graph title font size

# Create the bar graph with adjusted year labels
plot_data |>
  ggplot(aes(x = year_short, y = Mortality, fill = Gender)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  labs(
    title = "Mortality Numbers of Male Vs Female Decedents over 2007 to 2024",
    x = "Year (2000s)",
    y = "Number of Decedents"
  ) +
  scale_fill_manual(values = c("Male_decedents" = "blue", "Female_decedents" = "pink")) +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```
@fig-AvgAgeofDecedentsFemaleVSMale further examines the differences in average age at death between females and males. It is important to note that there are significantly more male deaths than female deaths, which could result in a lower average age for males due to the larger sample size. Although the graph does not definitively indicate whether males generally die at an older age than females or vice versa, it does suggest that the average age at death for males appears to be considerably higher than that for females during many periods indicated in the graph. More information is available in @sec-3-dpoint.

```{r}
#| label: fig-AvgAgeofDecedentsFemaleVSMale
#| fig-cap: Average Age of Death (Female VS Male)
#| echo: false
#| warning: false
#| message: false

@@

# Create the line graph for average age of death
avg_age_data |>
  ggplot(aes(x = year_short, y = Average_Age, color = Gender, group = Gender)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "Average Age of Death for Male Vs Female Decedents",
    x = "Year",
    y = "Average Age of Death"
  ) +
  scale_color_manual(values = c(
    "Average_age_of_death_male_decedents" = "blue",
    "Average_age_of_death_female_decedents" = "pink"
  )) +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

>>>>

# Create the bar graph with adjusted year labels
plot_data |>
  ggplot(aes(x = year_short, y = Mortality, fill = Gender)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  labs(
    title = "Mortality Numbers of Male Vs Female Decedents over 2007 to 2024",
    x = "Year (2000s)",
    y = "Number of Decedents"
  ) +
  scale_fill_manual(values = c("Male_decedents" = "blue", "Female_decedents" = "pink")) +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  ) +
  theme(plot.title = element_text(hjust = 0.5,size = 10))
```
@fig-AvgAgeofDecedentsFemaleVSMale further examines the differences in average age at death between females and males. It is important to note that there are significantly more male deaths than female deaths, which could result in a lower average age for males due to the larger sample size. Although the graph does not definitively indicate whether males generally die at an older age than females or vice versa, it does suggest that the average age at death for males appears to be considerably higher than that for females during many periods indicated in the graph. More information is available in @sec-3-dpoint.

```{r}
#| label: fig-AvgAgeofDecedentsFemaleVSMale
#| fig-cap: Average Age of Death (Female VS Male) 2007-2024
#| echo: false
#| warning: false
#| message: false

@@

# Create the line graph for average age of death
avg_age_data |>
  ggplot(aes(x = year_short, y = Average_Age, color = Gender, group = Gender)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "Average Age of Death for Male Vs Female Decedents",
    x = "Year (in 2000s)",
    y = "Average Age of Death"
  ) +
  scale_color_manual(values = c(
    "Average_age_of_death_male_decedents" = "blue",
    "Average_age_of_death_female_decedents" = "pink"
  )) +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```
